Computational musicology, ????, Profit

### 2016-07-31 paper.tex
Update thanks.
Avoid repeated phrase.

Such judgements are perilous from a musicological point of view, as they are often based on a jury's intuition as to
the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
the two compositions, for example in the manner Seaward and Matwin suggest for textual plaguerism\cite{Intrinsic Plaguerism Detection}.

@@

Finally, thank you to the generous people who read through early drafts of this paper and made many valuable suggestions.

>>>>

Such judgements are perilous from a musicological point of view, as they are often based on a jury's intuition as to
the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
the two compositions, as Seaward and Matwin suggest for textual plaguerism\cite{Intrinsic Plaguerism Detection}.

@@

Finally, thank you to the generous people who read drafts of this paper and made many valuable suggestions.
